Parsing Postfix log files

### 2009-02-23 doc/logparser-introduction.tex
Fixed the problem where \label{} and \ref{} didn't work properly with glossary chapters.

The bibliography contains references to the resources used in developing
the algorithm, writing the program, and preparing this thesis.  Also
listed are some additional resources expected to be helpful in
understanding \acronym{SMTP}, Postfix, anti-spam techniques, or the thesis.

>>>>

The bibliography (appendix~\ref{bibliography}) contains references to the
resources used in developing the algorithm, writing the program, and
preparing this thesis.  Also listed are some additional resources expected
to be helpful in understanding \acronym{SMTP}, Postfix, anti-spam
techniques, or the thesis.

### 2009-02-23 doc/logparser.tex
Annotated all URLs with last checked date.
Fixes for overfull hboxes.
Dealt with a couple of XXX items, and removed another couple because they're unimportant or I don't understand them any more.
Fixed the problem where \label{} and \ref{} didn't work properly with glossary chapters.

% Acronyms and glossary entries.  Useful options:
% * nonumberlist disables the list of page numbers after each entry.
\usepackage[acronym,toc,numberedsection=autolabel,style=list,nonumberlist]{glossaries}
\renewcommand{\glspostdescription}[0]{}
\renewcommand{\glsautoprefix}[1]{glossary:#1}
\newglossary[plg]{postfix}{pin}{pout}{Postfix Daemons}
\makeglossaries{}
\newcommand{\acronym}[1]{%
    \gls{#1}\glsadd{#1 glossary}%
}

@@

% Add last checked dates to all URLs
\newcommand{\urlLastChecked}[2]{%
    \url{#1} (last checked #2)%
}

@@

XXX WHY DOES $\backslash{}$ref\{\} NOT WORK PROPERLY FOR CHAPTERS IN THE APPENDIX\@?

XXX NEED A NAME FOR THE ARCHITECTURE, AND A DIFFERENT NAME FOR THE
IMPLEMENTATION\@.  Parse::FAR\@???

@@

XXX CHECK YEARS FOR BIBLIOGRAPHY ENTRIES\@.  WHAT DO I MEAN BY THIS\@?

XXX CHECK URLS FOR BIBLIOGRAPHY ENTRIES, AND UPDATE LAST CHECKED DATES\@.

@@

XXX ANNOTATE ALL URLS WITH LAST CHECKED DATE\@.

XXX STANDARDISE ON ``email'' OR ``mail'' EVERYWHERE\@?

XXX INVESTIGATE Doug Lenat.

@@

\label{Glossary}
\printglossary{}
\label{Acronyms}
\printglossary[type=\acronymtype]{}
\label{Postfix Daemons}
\printglossary[type=postfix]{}

>>>>

% Acronyms and glossary entries.  Useful options:
% * nonumberlist disables the list of page numbers after each entry.
\usepackage[acronym,toc,numberedsection=nolabel,style=list,nonumberlist]{glossaries}
\renewcommand{\glspostdescription}[0]{}
\renewcommand{\glsautoprefix}[1]{glossary:#1}
\newglossary[plg]{postfix}{pin}{pout}{Postfix Daemons}
\makeglossaries{}
\newcommand{\acronym}[1]{%
    \gls{#1}\glsadd{#1 glossary}%
}

@@

% Add last checked dates to all URLs
\newcommand{\urlLastChecked}[3][ ]{%
    \url{#2}#1(last checked #3)%
}

@@

@@

@@

@@

\renewcommand{\glossarypostamble}{\label{Glossary}}
\printglossary{}
\renewcommand{\glossarypostamble}{\label{Acronyms}}
\printglossary[type=\acronymtype]{}
\renewcommand{\glossarypostamble}{\label{Postfix Daemons}}
\printglossary[type=postfix]{}
